INForex: Interactive News Digest for Forex Investors

### 2022-01-05 paper.tex
Add makefiles, change url link, and rename files -- cjwang.

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf]{acmart}

%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% As of May 2020, [sigchi] and [sigchi-a] are no longer used. Please use sigconf (above) for SIGCHI conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for conferences using one-column small layout
% \documentclass[acmsmall,review]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{10.1145/1122445.1122456}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Online '20]{Online '20: 29th ACM International Conference on Information and Knowledge Management }{October 19--023, 2020}{Online}
\acmBooktitle{ }
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
% \title{INForex: An Interactive News Digestion for Forex Investors}
  \title{INForex: Interactive News Digest for Forex Investors}   % AMH: check

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

\author{Yi-Shyuan Chiang}
\authornote{These authors contributed equally to this work; author order was determined alphabetically.}
\email{yschiang@gapp.nthu.edu.tw}
\affiliation{%
  \institution{Research Center for Information Technology Innovation, Academia Sinica}
  \city{Taipei}
  \country{Taiwan}}

\author{Chih-Hen Lee}
\authornotemark[1]
\email{ch.lee@citi.sinica.edu.tw}
\affiliation{%
  \institution{Research Center for Information Technology Innovation, Academia Sinica}
  \city{Taipei}
  \country{Taiwan}}

\author{Chuan-Ju Wang}
\email{cjwang@citi.sinica.edu.tw}
\affiliation{%
  \institution{Research Center for Information Technology Innovation, Academia Sinica}
  \city{Taipei}
  \country{Taiwan}}

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Chiang, Lee, and Wang}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
As foreign exchange (Forex) markets reflect real-world events, locally or
globally,
financial news is often leveraged to predict Forex trends.
In this demonstration, we propose INForex, an interactive web-based system that
displays a Forex plot alongside related financial news.
To our best knowledge, this is the first system to successfully align the
presentation of two types of time-series data---Forex data and textual
news data---in a unified and time-aware manner. 
Specifically, we first present two event detection methods based on the
standard deviation (SD) and directional change (DC) of the Forex data and use
these to locate specific periods during which prices or trends in Forex markets
change dramatically.
Moreover, INForex includes a keyword filtering function with which users can
filter news with self-defined keywords.
The system can be of great help in revealing valuable insight and relations
between the two types of data and is thus valuable for decision making
not only for professional financial analysts or traders but also for common
investors.
The system is available online at~\url{http://chlee.pythonanywhere.com/forex/}.
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10003260.10003282</concept_id>
       <concept_desc>Information systems~Web applications</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Web applications}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{Forex, financial news, standard deviation, directional change}

%% A "teaser" image appears between the author and affiliation
%% information and the body of the document, and typically spans the
%% page.
\begin{teaserfigure}
  \includegraphics[width=\textwidth]{teaser.pdf}
  \caption{INForex available at~\url{http://chlee.pythonanywhere.com/forex/}}
  \Description{}
  \label{fig:teaser}
\end{teaserfigure}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\section{Introduction}
The foreign exchange (Forex) market has been one of the most popular financial
markets for decades, with an estimated \$1\ trillion traded every
day~\cite{YAO200079}.
Spot trading, currency options, currency futures, and currency exchange-traded
funds (ETFs) are four major ways to trade Forex~\cite{TradeForex}.
The strategies might vary but they are driven by an intuitive rule of thumb,
which is to buy low and sell high~\cite{KOOLEN2014144,Zervos11}.
Therefore, the crucial question is whether investors can accurately forecast 
prices or trends.

Forex markets are influenced by numerous factors, including producer price index
(PPI), interest rates, and politics.
In order to consider as many factors as possible to gain a more comprehensive
view for Forex investment, most investors stay informed by relying on news.
Besides the fact that news usually reflects real-world events, the similar
nature of news and Forex also makes these two co-dependent.
For example, if the Federal Reserve System (the Fed) cuts the interest rate, it is
more likely that the value of USD will drop; also, such a devaluation will
later be the subject of another piece of news~\cite{"CNBC"}.

Considering the critical role of news for Forex investment, in this
demonstration, we propose INForex, an interactive web-based system that
displays a Forex plot alongside related financial news.
With the proposed system we seek to align the timing of Forex and news data 
to highlight the connection between these two types of time-series data.
In INForex the release time of news stories is displayed as vertical lines on the
Forex plot to emphasize the order of breaking news and exchange rates. In
addition, when users hover on a vertical line, the background color of the
corresponding news changes. 
Moreover, we propose using two event detection methods based on the standard
deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to
locate specific periods during which the prices or trends in Forex markets change dramatically.
Via this design, we assist users by putting the focus on changes of trend or periods 
of large price volatility.
INForex also comes with a keyword filtering function that allows users to
filter news with self-defined keywords.
To our best knowledge, this is the first system that effectively visualizes these two
types of time-series data---Forex data and textual news data---in a
unified and time-aware manner. 
The proposed INForex can be of great help in revealing valuable insight and
relations between the two types of data and is thus valuable for
decision-making not only for professional financial analysts or traders but
also for common investors.

The remainder of this paper is organized as follows.
In Section~\ref{sec:related}, we review previous studies related to Forex and
news and major websites for Forex traders.
Section~\ref{sec:system} describes the proposed system with details related to
data collection, event detection algorithms, interface, and key features.
After that, we provide a case study in Section~\ref{sec:case}, and
conclude and suggest future work in Section~\ref{sec:conclude}.

\section{Related Work and Systems}\label{sec:related}
The dynamics between news and Forex markets have been explored from several
different aspects.
Evans and Lyons~(2005) prove that news can have significant effects on currency
for days~\cite{EVANS2005197}, and macro news can affect currency prices
directly and indirectly via order flow~\cite{EVANS200826}.
There is other evidence showing that news and Forex trend are correlated as well.
For instance, Bauwens et al.~(2005) show that volatility increases right
before the announcement of scheduled news and unscheduled-but-periodic
news~\cite{BAUWENS20051108}, whereas Chatrath et al.~(2014) suggest that prices
respond within a mere 5 minutes after the news release~\cite{CHATRATH201442}.
Keeping in mind how Forex markets and news interact, it is reasonable for traders
to begin their days by reading news commentary to determine the market
sentiment and the direction for trading~\cite{samuels2015trader}.

Apart from the literature discussing the relation between Forex and news, 
many trading websites provide useful information for Forex investors,
each of which has its own features and limitations~\cite{ForexWebsites}.
For instance, BabyPips\footnote{\url{https://www.babypips.com}} is a friendly
website for junior traders, providing not only Forex plots but also courses,
tutorials, and forums for beginners.
Bloomberg\footnote{\url{https://www.bloomberg.com}} is a well-known news
agency; thus, in addition to currency data and plots, it also provides various
categories of news for users to focus on.
TradingView\footnote{\url{https://www.tradingview.com}} provides numerous
functions in a page, including watchlist, alerts, headlines, and real-time chats,
where users can customize the settings. 
However, most of these websites do not put news and the Forex plot on the same
page, or do not explicitly align the news release times with the Forex prices.
Most neglect the time-dependent relation between news and Forex data
and thus do not effectively visualize these two types of time-series data in a
unified and time-aware manner.

\section{System Description}\label{sec:system}

\subsection{Data Collection}
The Forex data was collected from
philipperemy/FX-1-Minute-Data.\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}
For demonstration purposes, we chose the EUR/USD index and used the DateTime
Stamp, OPEN Bid Quote, HIGH Bid Quote, LOW Bid Quote, and CLOSE Bid Quote
columns to plot the Forex candlestick chart; moreover, the time span for the
Forex data is from August 4, 2019 to September 13, 2019, and the granularity of
data is minute. 
As for news, we crawled articles from The Wall Street
Journal,\footnote{\url{https://www.wsj.com}} each of which contains the title,
the source, the release time, and the corresponding URL.
In this demonstration, there are 1,116 articles in total.

\subsection{Event Detection Algorithms}\label{sec:algo}
The proposed system comes with two event detection algorithms: one based on
the standard deviation of Forex price differences (referred as SD events
hereafter) and one based on the directional change of Forex prices (referred
as DC events hereafter)~\cite{7850020}. 
Specifically, SD events indicate time points during which the Forex prices
dramatically change, whereas DC events show time points during which the trends of
Forex prices change.

We here briefly describe the two algorithms.
Let $P= [p_1, p_2, ..., p_n]$ denote a series of Forex prices, where $p_t$
stands for the CLOSE Bid Quote at minute~$t$ and $n$ equals the total
numbers of daily Forex data; also, the series of difference rates between two
Forex prices is defined as $\mathcal{D}= [d_1, d_2, ..., d_m]$, where $d_t =
{(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbb Z^+$ denotes the range in minutes.
Note that we set $w=20$ in our prototype system.
We first calculate the standard deviation of differences in list~$\mathcal{D}$
and denote this as $\sigma_\mathcal{D}$; we then use the $z$-score of each
difference to determine the events (i.e.,
$z_{d_i}=(|d_i-m_{\mathcal{D}}|)/\sigma_{\mathcal{D}}>\tau$), where
$m_{\mathcal{D}}$ denotes the mean of the list~$\mathcal{D}$.)
In this demonstration, we consider $\tau=1,2,3$ as our thresholds 
corresponding to labels \emph{Low}, \emph{Medium}, and \emph{High} in the
system. 
Note that a higher threshold locates fewer events.

As for the DC events, the market is summarized into a set of uptrend and
downtrend events~\cite{7850020}.
A DC event, which includes a start point and an end point, can be seen as a period
during which the trend starts to change.
Initially, we use the first element in the price list~$p_1$ as the starting point
of the algorithm; then, the algorithm starts looking through the price list~$P$
in a sequential manner until it locates a price~$p_c$ for which
$|{(p_c-p_1)}/{p_1}|>\theta$.
In this demonstration, we consider
$\theta=\sigma_{\mathcal{D}},2\sigma_{\mathcal{D}},3\sigma_{\mathcal{D}}$ as
our thresholds, corresponding to labels \emph{Low},
\emph{Medium}, and \emph{High} in the system.
If $p_c > p_1$, the span from $p_1$ to $p_c$ denotes an upward DC event;
otherwise, it is a downward DC event.
After finding the first DC event, we look for other DC events in the
rest of the price sequence.
Let us consider a market starting with a downtrend, meaning that the Forex market
is now in a downtrend and waiting for a next uptrend: we continue
updating the lowest price $p_\ell$ in this downtrend until we find a 
price~$p_k$ for which ${(p_k-p_\ell)}/{p_\ell}>\theta$. Then, we note that the span from
$p_\ell$ to $p_k$ is an upward DC event, and the trend becomes an upward one.
Similarly, if a market is in an uptrend, we continue to update the highest 
price~$p_h$ in this uptrend until we find a price~$p_k$ for which
${(p_h-p_k)}/{p_h}>\theta$, in which case the ``$p_h$-to-$p_c$'' spans a downward DC
event, and the trend becomes a downward one.
After finishing examining all the daily Forex data, we have a series of DC events.

\subsection{Interfaces and features}
The INForex interface can be divided into two main parts: 1) the Forex chart
(in the left panel of the system) and 2) the news section (the right panel).
Users customize the selection criteria either by directly
manipulating the Forex chart or applying keyword filters.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{hover.pdf}
  \caption{The interfaces of INForex. Note that news is highlighted when the cursor hovers over the
  corresponding timeline on the chart. The yellow interval is the news
  selection range which can be decided by users.}
  \label{fig:hover}
\end{figure}

\subsubsection{Interactive Forex Chart}
Forex prices are displayed by a standard candlestick chart, powered by
Plotly graphing
libraries.\footnote{\url{https://https://plotly.com/graphing-libraries/}}
Users specify the date they are interested in with the calendar icon above
the chart and then explore the chart freely by zooming in or dragging out the
time frame of interest.
Except for the Forex chart, the blue vertical lines correspond to the news story
release time points. 
As shown in Figure~\ref{fig:hover}, the corresponding news in the right panel
is highlighted if users hover over the corresponding blue line on the chart.
Users also link to the original posts and websites by clicking on the news
cards.
Moreover, users can easily spot specific time ranges of interest
by single-clicking the start and end points of a period on the Forex chart
(resulting in the yellow span in the figure); the news section in the right
panel changes correspondingly according to the selected time span.

\subsubsection{Forex Event Identifier}
Users specify event types (i.e., SD or DC)  and the corresponding thresholds (i.e., Low, Medium, or High) with the Forex event identifier (see the buttoms below the date selection calendar in Figure~\ref{fig:hover}), after which the algorithm output is shown on the Forex chart as
gray dots for the SD events and span lines for the DC events (e.g., see
Figures~\ref{fig:SD} and~\ref{fig:DC} for examples of SD and DC events,
respectively).
For example, users specify August 30, 2019 and select the ``SD'' event with
the ``Low'' threshold; from the upper panel of Figure~\ref{fig:SD}, users 
observe a dramatic change from 14:30 to 16:30 on this day (see the red box in the figure) and 
proceed to select a specific time range on the plot. 
In return, the news section displays related news such as ``Would Warren
Buffett Buy Greenland?'' and ``Risky Seller Financing Flourishes Where Homes
Are Cheapest''. 
Note that once done with a specific setting, users clear the setting with
the ``clear all'' button on the top-right of the left panel;
a higher threshold (the lower panels in Figures~\ref{fig:SD}
and~\ref{fig:DC}) locates fewer events.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sd.pdf}
  \caption{Display of SD events on August 30, 2019. The upper panel
  is set to the ``Low'' threshold and the lower one is set to the ``High''
  threshold.}
  \Description{}
  \label{fig:SD}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{dc.pdf}
  \caption{Display of DC events on August 30, 2019. Upper panel
  set to ``Low'', lower panel to ``High''.}
  \Description{}
  \label{fig:DC}
\end{figure}

\subsubsection{Customizable Keyword Filter
}
If users are interested in more specific news, they use the tags under the
plot to filter out news with selected keywords.
As examples, we have placed several major keywords such as ``U.S.'' and ``Trump'';
users customize their own tags by clicking the ``+'' button.
Figure~\ref{fig:keywords} shows the displayed news based on different keywords
and time filters.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{news.pdf}
  \caption{Filtering news on August 30, 2019. From left to right
  are none, keyword: ``U.S.'', time: `14:30--16:30', and both.}
  \Description{}
  \label{fig:keywords}
\end{figure}

\section{Case Study}\label{sec:case}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{case.pdf}
  \caption{Case study}
  \Description{}
  \label{fig:case}
\end{figure}

In this section, we provide an example to show the strong relation among
events, news, and Forex, as shown in Figure~\ref{fig:case}.
On August 6, 2019, we see that the ``Welcome to Turnaround Tuesday''
article released at 08:43, the time when an uptrend is about to end; note that the DC
event with the High threshold shows that this uptrend starts at 05:07.
The news mentions ``U.S. stock futures were in a decidedly better mood as
Tuesday began than on Monday'', indicating that U.S. stock is likely to rebound
later, thus causing appreciation on USD.
Then, the EUR/USD starts a downtrend from 08:49 to 14:41.
Note lower rates for EUR/USD could be due to a relatively high value for USD.

\section{Conclusion and Future work}\label{sec:conclude}
In this paper, we propose INForex, an interactive system that aligns the
presentation of Forex data and textual news data in a unified and
time-aware manner.
By placing the chart and related news side by side, users, financial
professionals, and amateur investors all understand Forex trends
quicker and easier.
Beyond the presentation in this paper, we are now working toward providing
real-time news updates in the system.
In addition, with the collected browsing behavior from users, we hope to
provide more customized news feed via a personalized news recommender system
by leveraging machine learning and natural language processing techniques.

\section{Acknowledgments}
We thank Po-Chuan Chien for collecting the news articles and Chen-Hung Pai for providing valuable comments regarding the design of the proposed system.
This project was supported in part by the Ministry of Science and Technology in Taiwan under the grants MOST 108-2218-E-009-049.

\bibliographystyle{ACM-Reference-Format}
\bibliography{reference}

\end{document}
\endinput
%%
%% End of file `sample-sigconf.tex'.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{times}
\usepackage{soul}
\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[small]{caption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{bbm}
\urlstyle{same}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{INForex: Interactive News Digest for Forex Investors}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Chih-Hen Lee\inst{1}\and
Yi-Shyuan Chiang\inst{2} \and
Chuan-Ju Wang\inst{3}}
%
\authorrunning{Lee et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Research Center for Information Technology Innovation, \\Academia Sinica, Taipei, Taiwan\\
\email{\{\inst{1}ch.lee, \inst{3}cjwang\}@citi.sinica.edu.tw} \\
\email{\inst{2}yschiang@gapp.nthu.edu.tw}
\\}
%
\maketitle              % typeset the header of the contribution
%
\vspace{-0.6cm}
\begin{abstract}
As foreign exchange (Forex) markets reflect real-world events, locally or globally, financial news is often leveraged to predict Forex trends. 
In this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside related financial news. To our best knowledge, this is the first system to successfully align the presentation of two types of time-series data---Forex data and textual news data---in a unified and time-aware manner and as well as the first Forex-related online system leveraging deep learning techniques. 
The system can be of great help in revealing valuable insights and relations between the two types of data and is thus valuable for decision making not only for professional financial analysts or traders but also for common investors.
The system is available online at~\url{http://cfda.csie.org/forex/}, and the introduction video is at~\url{https://youtu.be/ZhFqQamTFY0}.

\keywords{FOREX  \and Attention Mechanism \and Web System.}
\end{abstract}
%
%
%
\vspace{-0.8cm}
\section{Introduction}
\vspace{-0.3cm}
Forex markets are influenced by numerous factors, including gross domestic product (GDP), interest rates, and politics.
In order to consider as many factors as possible to gain a more comprehensive view for Forex investment, most investors stay informed by relying on news.

Considering the critical role of news for Forex investment, in this demonstration, we propose INForex, an interactive web-based system that displays a Forex plot alongside related financial news. With the proposed system we seek to align the timing of Forex and news data to highlight the connection between these two types of time-series data. In INForex the release time of news stories is displayed as vertical lines on the Forex plot to emphasize the order of breaking news and exchange rates. Also, when users hover on a vertical line, the background color of the corresponding news will change.

Moreover, we propose using two event detection methods based on the standard deviation (SD) and directional change (DC)~\cite{7850020} of the Forex data to locate specific periods during which the prices or trends in Forex markets change dramatically.
Via this design, we assist users to make trading strategies by putting the focus on changes of trend or periods of large price volatility.
In addition, with the great advancement in natural language processing (NLP) and deep learning (DL) in recent years, in the proposed system, we utilize attention mechanisms~\cite{attention} to further exploit the semantics in financial news.
Specifically, by leveraging the financial news as training corpus and the aforementioned DC events as labels, our proposed system train an attention-based classification model that can be used to highlight worth-noting news and the potential keywords to users.
Last but not least, INForex also comes with a keyword filtering function that allows users to filter news with self-defined keywords, where they can focus on searching related news of their interests.

To our best knowledge, this is the first system that effectively visualizes these two types of time-series data---Forex data and textual news data---in a unified and time-aware manner and as well as the first Forex system leveraging deep learning techniques. 
The proposed INForex can be of great help in revealing valuable insight and relations between the two types of data and is thus valuable for decision-making not only for professional financial analysts or traders but also for common investors.

\vspace{-0.5cm}
\section{System Description}\label{sec:system}
\vspace{-0.9cm}
\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{hover.pdf}
  \caption{The interfaces of INForex. Note that news is highlighted when the cursor hovers over the
  corresponding timeline on the chart.}
  \label{fig:hover}
\end{figure}\
\vspace{-1.7cm}

\subsection{Data Collection}
\vspace{-0.3cm}
The Forex data was collected from
philipperemy/FX-1-Minute-Data.\footnote{\url{https://github.com/philipperemy/FX-1-Minute-Data}}
The training period is from January 1, 2010 to December 31, 2018, and the testing period is from August 4, 2019 to September 13, 2019 (which is the time span shown in the system).

As for news, we crawled articles from The Wall Street
Journal,\footnote{\url{https://www.wsj.com}}. Following the above setting, we separate these news into training, validation, and testing sets, the number of news corresponds to which are 80,000, 2,766, and 1,021, respectively
Note that the validation set is the last 2,766 news in the training period, and only the testing batch of news is displayed on our system.
\vspace{-0.5cm}
\subsection{Event Detection Algorithms}\label{sec:algo}
\vspace{-0.2cm}
The proposed system comes with two event detection algorithms: one based on
the standard deviation of Forex price differences (referred as SD events hereafter) and one based on the directional change of Forex prices (referred
as DC events hereafter)~\cite{7850020}. 
Specifically, SD events indicate time points during which the Forex prices
dramatically change, whereas DC events show time points where the trends of
Forex prices change.

We here briefly describe the two algorithms.
Let $P= [p_1, p_2, ..., p_n]$ denote a series of Forex prices, where $p_t$
stands for the CLOSE Bid Quote at minute~$t$ and $n$ equals the total
numbers of daily Forex data; also, the series of difference rates between two
Forex prices is defined as $\mathcal{D}= [d_1, d_2, ..., d_m]$, where $d_t =
{(p_{t+w}-p_t)}/{p_t}$ and $w\in\mathbbm{Z}^+$ denotes the range in minutes.
Note that we set $w=20$ in our prototype system.
We first calculate the standard deviation of differences in list~$\mathcal{D}$
and denote this as $\sigma_\mathcal{D}$; we then use the $z$-score of each
difference to determine the events (i.e.,
$z_{d_i}=(|d_i-m_{\mathcal{D}}|)/\sigma_{\mathcal{D}}>\tau$), where
$m_{\mathcal{D}}$ denotes the mean of the list~$\mathcal{D}$.)
In this demonstration, we consider $\tau=1,2,3$ as our thresholds 
corresponding to labels \emph{Low}, \emph{Medium}, and \emph{High} in the
system. 
Note that a higher threshold locates fewer events.

As for the DC events, the market is summarized into a set of uptrend and
downtrend events~\cite{7850020}.
A DC event, which includes a start point and an end point, can be seen as a period
during which the trend starts to change.
Initially, we use the first element in the price list~$p_1$ as the starting point; then, the algorithm starts looking through the price list~$P$
in a sequential manner until it locates a price~$p_c$ for which
$|{(p_c-p_1)}/{p_1}|>\theta$.
In this demo, we consider
$\theta=\sigma_{\mathcal{D}},2\sigma_{\mathcal{D}},3\sigma_{\mathcal{D}}$ as
our thresholds, corresponding to labels \emph{Low},
\emph{Medium}, and \emph{High} in the system.
If $p_c > p_1$, the span from $p_1$ to $p_c$ denotes an upward DC event;
otherwise, it is a downward DC event.
After finding the first DC event, we look for other DC events in the
rest of the price sequence.
\vspace{-0.5cm}
\subsection{Attention Model}
\vspace{-0.3cm}
In this subsection, we introduce the pipeline of our model in detail. First, we represent each word in news titles and content with the pre-trained embedding from GloVe.\footnote{\url{https://nlp.stanford.edu/projects/glove/}}
We later construct an attention layer~\cite{attention}
to aggregate the words embeddings in each news into one document embedding for each news.
According to~\cite{attention}, the attention mechanism is formulated as ${\rm Attention}(Q, K, V) = {\rm softmax}(QK\textsuperscript{T}/\sqrt{d_k})V$, where $d_k$ is the dimension of keys and queries. In our settings, the queries($Q$) are initially randomized, while the keys($K$) and values($V$) are the GloVe embeddings for words. Here, the main concept is that every word contributes to the document embeddings by different levels; therefore, if a word accounts for a much greater weight than other words in the document do, it might be a potential keyword. After getting the document embeddings, we first apply a ReLU activation function, and then pass the embeddings to a linear classification layer to predict the final label. In terms of labeling training data, a piece of news is labeled as positive when there is a start of any high-threshold DC event in the interval ${(t, t+30)}$, where $t$ is the news release time in minutes. Otherwise, it will be labeled as negative.

Other experimental details are listed as follows.
We implement the model under the PyTorch\footnote{\url{https://pytorch.org/}} framework. To reduce the training time, we only use the first 200 words in the concatenated news title and content as the textual input. For the training process, we select Adam~\cite{Adam} as the optimizer with learning rate 0.0001, and train data with 120 epochs and batch size 20.
\vspace{-0.5cm}
\subsection{Interfaces and features}
\vspace{-0.3cm}
The INForex interface can be divided into two main parts: 1) the Forex chart
(in the left panel of the system) and 2) the news section (the right panel).

\vspace{-0.2cm}
\subsubsection{Interactive Forex Chart}
\vspace{-0.2cm}
Forex prices are displayed by a standard candlestick chart, powered by
Plotly graphing
libraries.\footnote{\url{https://https://plotly.com/graphing-libraries/}}
Users can specify the date they are interested in with the calendar icon above
the chart and then explore the chart freely by zooming in or dragging out the
time frame of interest.
Except for the Forex chart, the blue vertical lines correspond to the news story
release time points. 
As shown in Figure~\ref{fig:hover}, the corresponding news in the right panel
is highlighted if users hover over the corresponding blue line on the chart.
Moreover, users can easily spot specific time ranges of interest
by single-clicking the start and end points of a period on the Forex chart
(resulting in the yellow span in the figure); the news section in the right
panel changes correspondingly according to the selected time span.

\vspace{-0.4cm}
\subsubsection{Forex Event Identifier}
\vspace{-0.2cm}
Users specify event types (i.e., SD or DC)  and the corresponding thresholds (i.e., Low, Medium, or High) with the Forex event identifier (see the buttoms below the date selection calendar in Figure~\ref{fig:hover}), after which the algorithm output is shown on the Forex chart as
gray dots for the SD events and span lines for the DC events.
Note that once done with a specific setting, users clear the setting with
the ``clear all'' button on the top-right of the left panel;
a higher threshold locates fewer events.

\subsubsection{Attention Weight Visualization}
\vspace{-1.3cm}
\begin{figure*}
  \centering
  \includegraphics[width=0.7\linewidth]{weights.pdf}
  \caption{Attention weights. The word ``clashes'' is a dark red word, ``pessimism'' and ``tariff'' are red words, and ``Beating'' and ``statisticians'' are pink words.}

  \label{fig:weights}
\end{figure*}
\vspace{-0.7cm}
If a news is predicted as positive (i.e., potentially highly correlated with the DC events), the news title is highlighted in red.
After clicking the positive news title, a window showcasing the news title and content with highlighted keywords will pop up.
Here, three classes of keywords are defined. Let $\ell$ be the word count of a concatenated news title and content, and the maximum of $\ell$ is set to 200 as mentioned above. The dark red words are the most worth-noting words whose attention weights are greater than ${40}/{\ell}$, while the attention weights of red words and pink words are greater than ${20}/{\ell}$ and ${10}/{\ell}$, respectively.
As shown in Figure~\ref{fig:weights}, our model is able to capture keywords related to the Forex market in this case.
\vspace{-0.5cm}
\section{Conclusion and Future Work}\label{sec:conclude}
\vspace{-0.3cm}
In this paper, we propose INForex, an interactive system that aligns the Forex data and textual news data in a unified and
time-aware manner.
By placing the chart and related news side by side and displaying the potential keywords, users, financial
professionals, and amateur investors can all understand Forex trends
quicker and easier.

With limited financial resources, we can only propose a static prototype system with data made available online. However, since the real-time feature is crucial for investors, we will thrive to make INForex become a real-time system in the future, either with real-time industrial APIs.
We hope that this demonstration can facilitate more research on predicting Forex markets through deep learning models in the future.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

\bibitem{7850020}
Amer Bakhach and Edward P. K. Tsang and Hamid Jalalian: Forecasting directional changes in the FX markets. In: Proceedings of the 2016 IEEE Symposium Series on Computational Intelligence (SSCI), pp. 1--8. (2010)

\bibitem{attention}
Vaswani, Ashish and Shazeer, Noam and Parmar, Niki and Uszkoreit, Jakob and Jones, Llion and Gomez, Aidan N and Kaiser, \L ukasz and Polosukhin, Illia: Attention is All you Need. In: Proceedings of the 31st International Conference on Neural Information Processing Systems (NeurIPS), pp. 6000--6010. (2017)

\bibitem{Adam}
Diederik P. Kingma and Jimmy Ba: Adam: A Method for Stochastic Optimization. In: Proceedings of the 3rd International Conference on Learning Representations (ICLR) (2015)

\end{thebibliography}
\end{document}
